\sysfull

### 2017-08-03 paper/compiler.tex
Kiwan's compiler section revised - really nice text Kiwan

Each edge holds the information about the {\em live variables} across the edge\todo{Define live variables}{Kiwan}, and if the edge is within any loop, the {\em loop count}. By this information, the compiler tries to minimize the number of protected variable (viz. O2), because placing boundary at an edge means the live variables across that edge need to be protected. Also the compiler avoids placing boundaries at an edge that is within a loop whose loop count is big (viz. O3).

>>>>

Each edge holds the information about the {\em live variables} across the edge, and if the edge is within any loop, the {\em loop count}. By this information, the compiler tries to minimize the number of protected variable (viz. O2), because placing boundary at an edge means the live variables across that edge need to be protected. Also the compiler avoids placing boundaries at an edge that is within a loop whose loop count is big (viz. O3).
